Automated Assessment of Residual Plots with Computer Vision Models

### 2025-07-25 paper.Rmd
Upload cover letter

Consistent with this, the computer vision model assigns a distance $\hat{D}$ above the 95% quantile of the null distribution ($p-\text{value} = 0.00498$), leading to rejection of $H_0$. The bootstrapped distribution further supports this, with most fitted models also being rejected. In contrast, the RESET and Breusch-Pagan tests yield $p$-values above $0.3$, suggesting no violation. Only the Shapiro-Wilk test rejects normality with a small $p$-value.

>>>>

Consistent with this, the computer vision model assigns a distance $\hat{D}$ above the 95% quantile of the null distribution ($p\text{-value} = 0.00498$), leading to rejection of $H_0$. The bootstrapped distribution further supports this, with most fitted models also being rejected. In contrast, the RESET and Breusch-Pagan tests yield $p$-values above $0.3$, suggesting no violation. Only the Shapiro-Wilk test rejects normality with a small $p$-value.
